\Large \bf Uncovering Bugs in Distributed Storage Systems\\during Testing (not in Production!)

### 2015-12-23 experience.tex
update
update in case studies

\subsection{Live Table Migration}
%\subsection{Live \Azure Table Migration}
\label{sec:cases:migration}

The Live Table Migration library (MigratingTable) is designed to \emph{transparently} migrate a data set between tables in a
%The Live \Azure Table Migration library (MigratingTable) is designed to \emph{transparently} migrate a data set between tables in an
\Azure Storage service \emph{while} an application is accessing this data set. This case study is particularly interesting because its developers \emph{co-developed} the system with its \psharp test harness to increase confidence in the system. Indeed, this co-development process resulted in the discovery of several tricky bugs before the system went into production (see \S\ref{sec:eval}). The MigratingTable testing effort differs from the vNext case study: the vNext developers focused on specifying a single liveness property, while the MigratingTable test checks complete compliance with an interface (safety) specification.

\textbf{Specifics of the system}.
MigratingTable provides a \emph{virtual table} that has an interface similar to an ordinary \Azure table. This interface is named \texttt{IChainTable}. A virtual table is backed by a pair of \emph{old} and \emph{new} \emph{backend} tables, both of which implement \texttt{IChainTable}. A \emph{migrator} job is responsible for moving all data from the old table to the new table in the background. Meanwhile, each read and write operation issued to the virtual table is translated to a sequence of reads and writes on the backend tables according to a protocol, which intends to guarantee that when multiple applications issue \emph{input} operations to virtual tables that are backed by the same backend tables, the output is compliant with the specification of \texttt{IChainTable} for the combined \emph{input history} as if all the operations were done on a single table. The goal of using \psharp was to systematically test this property.

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{img/mocked_migration}
\caption{Environment model of MigratingTable (each box with a dotted line represents one \psharp machine). \PTComment{Change Reference Table to SpecTable}}
\label{fig:mockedmigration}
\end{figure}

\textbf{Testing challenges}.
There are two main challenges behind testing MigratingTable: the system is highly concurrent; and there are many possible input histories. The developers could have chosen specific input histories to test, but they were not confident that this approach would be effective in catching bugs, especially because concurrency increases the potential for difficult-to-foresee interactions between seemingly independent parts of the code. Instead, the developers wrote an in-memory reference implementation of the \texttt{IChainTable} specification, called \texttt{SpecTable}, to which the MigratingTable output on an arbitrary input history can be compared.
\PTComment{Suggested rephrasing: Instead, the developers wrote a more straightforward reference implementation of the \texttt{IChainTable} specification, called \texttt{SpecTable}, which is backed by a single in-memory table. 
 After executing an arbitrary input history on both implementations, the outputs can be compared to ensure that MigratingTable produces the same output as \texttt{SpecTable}.}

\textbf{Modeling and testing with \psharp}.
Figure~\ref{fig:mockedmigration} illustrates the \psharp test harness of MigratingTable. The test harness consists of a collection of \texttt{Service} machines that contain identically configured instances of MigratingTable; a \texttt{Tables} machine, which contains the old and new tables, and an instance of \texttt{SpecTable}; and a \texttt{Migrator} machine that performs the background migration. Each \texttt{Service} machine issues a random sequence of input operations to its MigratingTable, which then sends these operations to the \texttt{Tables} machine.

@@

\PTComment{I re-worded this para. See what you think.} Conceptually, the \psharp test harness randomly chooses (uniformly) an input history from a set that contains all possible input histories under a certain bound \PTComment{What bound?}. Assuming that any given bug in MigratingTable can manifest under at least one of the input histories in the set (the small scope hypothesis), then an execution of the test harness must have a non-negative probability of detecting the bug.

>>>>

\subsection{Live \Azure Table Migration}
\label{sec:cases:migration}

Live \Azure Table Migration (MigratingTable) is a library designed to \emph{transparently} migrate a data set between tables in an \Azure Storage service \emph{while} an application is accessing this data set. This case study is particularly interesting because MigratingTable was \emph{co-developed} with its \psharp test harness. This co-development process resulted in the discovery of several tricky bugs before the system went into production (see \S\ref{sec:eval}). The MigratingTable testing effort differs from the vNext case study: the vNext developers focused on a single liveness property, while the MigratingTable test harness checks complete compliance with an interface (safety) specification.

MigratingTable provides a \emph{virtual table} that has an interface similar to an ordinary \Azure table. This interface is named \texttt{IChainTable}. A virtual table is backed by a pair of \emph{old} and \emph{new} \emph{backend} tables, both of which implement \texttt{IChainTable}. A \emph{migrator} job is responsible for moving all data from the old table to the new table in the background. Meanwhile, each read and write operation issued to the virtual table is translated to a sequence of reads and writes on the backend tables according to a protocol, which intends to guarantee that when multiple applications issue \emph{input} operations to virtual tables that are backed by the same backend tables, the output is compliant with the specification of \texttt{IChainTable} for the combined \emph{input history} as if all the operations were done on a single table. The goal of using \psharp was to systematically test this property.

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{img/mocked_migration}
\caption{The \psharp test harness of MigratingTable (each box with a dotted line represents one \psharp machine).}
\label{fig:mockedmigration}
\end{figure}

There are two main challenges behind testing MigratingTable: (i) the system is highly concurrent; and (ii) there are many possible input histories. The developers could have chosen specific input histories to test, but they were not confident that this approach would be effective in catching bugs, especially because concurrency increases the potential for difficult-to-foresee interactions between seemingly independent parts of the code. Instead, the developers created a reference implementation of the \texttt{IChainTable} specification, called \texttt{SpecTable}, which is backed by a single in-memory table. After executing an arbitrary input history on both implementations, the outputs can be compared to ensure that MigratingTable produces the same output as \texttt{SpecTable}.

Figure~\ref{fig:mockedmigration} illustrates the \psharp test harness of MigratingTable. The harness consists of a set of \texttt{Service} machines that contain identically configured instances of MigratingTable; a \texttt{Tables} machine, which contains the old and new tables, and an instance of \texttt{SpecTable}; and a \texttt{Migrator} machine that performs the background migration. Each \texttt{Service} machine issues a random sequence of input operations to its MigratingTable, which then sends these operations to the \texttt{Tables} machine.

@@

Conceptually, the \psharp test harness randomly chooses (uniformly) an input history from a set that contains all possible input histories under a certain bound \PTComment{What bound?}. Assuming that any given bug in MigratingTable can manifest under at least one of the input histories in the set (the small scope hypothesis), then an execution of the test harness must have a non-zero probability of detecting the bug.
